\large{Vipassana for Hackers} \\ \Huge{Paper Two: The Brain} \\ \large\textit{Version 0.3}

### 2019-10-19 paper-two/paper-two.tex
removing 404 pdf, build for 0.3 public release
cleaning up acknowledgements

\title{%
  \large{Vipassana for Hackers} \\
  \Huge{Paper Two: The Brain} \\
  \large\textit{Version 0.2}
}
\author{Preethi Govindarajan}
\email[Correspondence email address: ]{preethi@deobald.ca}
\affiliation{Siggu.org}
\date{\today}

@@

\listoftodos

@@

To do this, the PPC receives input from auditory, visual, and somatosensory
systems, integrates this input, and uses the aggregate to activate the DL-PFC and motor cortex and is
involved in the performance of attention related tasks as well as higher-order motor
tasks such as grasping and catching. \cite{parietallobesa,parietallobes}

@@

Thank you to Steven Deobald for reviews, edits, and corrections.

``Brain\_human\_normal\_inferior\_view'' By Patrick J. Lynch, medical illustrator, CC BY
2.5, https://commons.wikimedia.org/w/index.php?curid=1496648

``Brain\_human\_lateral\_view.svg'' By Patrick J. Lynch, medical illustrator, CC BY
2.5, https://commons.wikimedia.org/w/index.php?curid=1496651

@@

\bibitem{ipl}
 Radua J, Phillips ML, Russell T, Lawrence N, Marshall N, Kalidindi S, El-Hage W, McDonald C,
 Giampietro V, Brammer MJ, David AS, Surguladze SA.
 \textit{Neural response to specific components of fearful faces in healthy
  and schizophrenic adults.}
  Neuroimage. 2010 Jan 1;49(1):939-46. doi: 10.1016/j.neuroimage.2009.08.030.
  Epub 2009 Aug 20.
  \url:https://www.ncbi.nlm.nih.gov/pubmed/19699306

@@

\bibitem{parietallobesa}
  Caspers S, Amunts K, Zilles K.
  \textit {Posterior Parietal Cortex: Multimodal Association Cortex.}
   The Human Nervous System. 3rd ed. New York: Elsevier; 2012.

\bibitem{parietallobes}
  Martin, R. E.
  \textit{Let’s Get to Know the Parietal Lobes!}
  \url{http://gablab.mit.edu/downloads/Parietal_Primer.pdf}
  \todo{parietal lobes article returns a 404. fix.}

@@

\bibitem{cortexbliss}
  Picard, Fabienne.
  \textit{State of belief, subjective certainty and bliss as a product of cortical
          dysfunction}
  Cortex, Volume 49, Issue 9, Pages 2494–2500ISSN 0010 9452,
  \url: https://doi.org/10.1016/j.cortex.2013.01.006. 2013.

@@

>>>>

\title{%
  \large{Vipassana for Hackers} \\
  \Huge{Paper Two: The Brain} \\
  \large\textit{Version 0.3}
}
\author{Preethi Govindarajan}
\email[Correspondence email address: ]{preethi@deobald.ca}
\affiliation{Siggu.org}
\date{\today}

@@

% \listoftodos

@@

To do this, the PPC receives input from auditory, visual, and somatosensory
systems, integrates this input, and uses the aggregate to activate the DL-PFC and motor cortex and is
involved in the performance of attention related tasks as well as higher-order motor
tasks such as grasping and catching. \cite{parietallobes}

@@

Thank you to Steven Deobald for reviews, edits, and corrections. \texttt{Brain\_human\_normal\_inferior\_view.svg} and
\texttt{Brain\_human\_lateral\_view.svg} by Patrick J. Lynch, medical illustrator, CC-BY 2.5 \cite{brainsvg}

@@

\bibitem{ipl}
 Radua J, Phillips ML, Russell T, Lawrence N, Marshall N, Kalidindi S, El-Hage W, McDonald C,
 Giampietro V, Brammer MJ, David AS, Surguladze SA.
 \textit{Neural response to specific components of fearful faces in healthy
  and schizophrenic adults.}
  Neuroimage. 2010 Jan 1;49(1):939-46. doi: 10.1016/j.neuroimage.2009.08.030.
  Epub 2009 Aug 20.
  \url{https://www.ncbi.nlm.nih.gov/pubmed/19699306}

@@

\bibitem{parietallobes}
  Caspers S, Amunts K, Zilles K.
  \textit {Posterior Parietal Cortex: Multimodal Association Cortex.}
   The Human Nervous System. 3rd ed. New York: Elsevier; 2012.

@@

\bibitem{cortexbliss}
  Picard, Fabienne.
  \textit{State of belief, subjective certainty and bliss as a product of cortical
          dysfunction}
  Cortex, Volume 49, Issue 9, Pages 2494–2500ISSN 0010 9452,
  \url{https://doi.org/10.1016/j.cortex.2013.01.006}. 2013.

@@

\bibitem{brainsvg}
  Patrick J. Lynch
  \texttt{Brain\_human\_normal\_inferior\_view.svg} and \textit{Brain\_human\_lateral\_view.svg}
  CC-BY 2.5
  \url{https://commons.wikimedia.org/w/index.php?curid=1496651}
  \url{https://commons.wikimedia.org/w/index.php?curid=1496648}
